Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2021-09-14 AttackTolerance/preprint/source/paper.tex
Move AttackTolerance to subfolder.

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
\usepackage{setspace} 
\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

\usepackage{booktabs} % For formal tables
\usepackage{epigraph}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont} % http://ctan.org/pkg/pifont
\usepackage{amsthm}

%% Include all macros below

@@

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Towards attack tolerant networks: concurrent multipath routing and the butterfly network} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Edward L. Platt\textsuperscript{1,*},
Daniel M. Romero\textsuperscript{1}
\\
\bigskip
\textbf{1} School of Information, University of Michigan, Ann Arbor, Michigan, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.

% Current address notes
%\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* elplatt@umich.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
evelopment of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}

@@

\begin{figure}[!h]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

We define the {\em bounded trust model} on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing communicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[height=3in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wraparound butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure*}[h!]
\centerline{\includegraphics[width=5in,height=5in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure*}

@@

\begin{figure}[h!]

@@

\begin{figure}[!h]
\begin{center}
\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

@@

\nolinenumbers

%\bibliography{references}

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{sterbenz_resilience_2010}
Sterbenz JP, Hutchison D, Çetinkaya EK, Jabbar A, Rohrer JP, Schöller M,
  et~al.
\newblock Resilience and survivability in communication networks: {Strategies},
  principles, and survey of disciplines.
\newblock Computer Networks. 2010;54(8):1245--1265.

\bibitem{barabasi_scale-free_2009}
Barabási AL, {others}.
\newblock Scale-free networks: a decade and beyond.
\newblock Science. 2009;325(5939):412.

\bibitem{albert_error_2000}
Albert R, Jeong H, Barabási AL.
\newblock Error and attack tolerance of complex networks.
\newblock Nature. 2000;406(6794):378--382.

\bibitem{nayak_different_2010}
Nayak GN, Samaddar SG.
\newblock Different flavours of man-in-the-middle attack, consequences and
  feasible solutions.
\newblock In: Computer {Science} and {Information} {Technology} ({ICCSIT}),
  2010 3rd {IEEE} {International} {Conference} on. vol.~5. IEEE; 2010. p.
  491--495.

\bibitem{grewal_caveat_2013}
Grewal GS, Ryan MD, Bursuc S, Ryan PY.
\newblock Caveat coercitor: {Coercion}-evidence in electronic voting.
\newblock In: Security and {Privacy} ({SP}), 2013 {IEEE} {Symposium} on. IEEE;
  2013. p. 367--381.

\bibitem{elmer-dewitt_first_1993}
Elmer-Dewitt P, Jackson D.
\newblock First nation in cyberspace.
\newblock Time. 1993;6:62--64.

\bibitem{baran_distributed_1964}
Baran P, {others}.
\newblock On distributed communications.
\newblock Volumes I-XI, RAND Corporation Research Documents, August. 1964; p.
  637--648.

\bibitem{dainotti_analysis_2011}
Dainotti A, Squarcella C, Aben E, Claffy KC, Chiesa M, Russo M, et~al.
\newblock Analysis of country-wide internet outages caused by censorship.
\newblock In: Proceedings of the 2011 {ACM} {SIGCOMM} conference on {Internet}
  measurement conference. ACM; 2011. p. 1--18.

\bibitem{christianson_why_1997}
Christianson B, Harbison WS.
\newblock Why isn't trust transitive?
\newblock In: Security protocols. Springer; 1997. p. 171--176.

\bibitem{zin_survey_2015}
Zin SM, Anuar NB, Kiah MLMM, Ahmedy I.
\newblock Survey of secure multipath routing protocols for {WSNs}.
\newblock J Netw Comput Appl. 2015;55:123--153.

\bibitem{barabasi_emergence_1999}
Barabási AL, Albert R.
\newblock Emergence of scaling in random networks.
\newblock Science. 1999;286(5439):509--512.

\bibitem{hunter_pakistan_2008}
Hunter P.
\newblock Pakistan {YouTube} block exposes fundamental internet security
  weakness: {Concern} that pakistani action affected youtube access elsewhere
  in world.
\newblock Computer Fraud \& Security. 2008;2008(4):10--11.

\bibitem{poulsen_edward_2013}
Poulsen K.
\newblock Edward {Snowden}’s e-mail provider defied {FBI} demands to turn
  over crypto keys, documents show.
\newblock WIRED. 2013;.

\bibitem{zimmermann_official_1995}
Zimmermann PR.
\newblock The official {PGP} user's guide.
\newblock MIT press; 1995.

\bibitem{richters_trust_2011}
Richters O, Peixoto TP.
\newblock Trust transitivity in social networks.
\newblock PloS one. 2011;6(4):e18384.

\bibitem{avizienis_basic_2004}
Avizienis A, Laprie JC, Randell B, Landwehr C.
\newblock Basic concepts and taxonomy of dependable and secure computing.
\newblock IEEE T Depend Secure. 2004;1(1):11--33.

\bibitem{von_neumann_probabilistic_1956}
Von~Neumann J.
\newblock Probabilistic logics and the synthesis of reliable organisms from
  unreliable components.
\newblock Automata studies. 1956;34:43--98.

\bibitem{qadir_exploiting_2015}
Qadir J, Ali A, Yau KLA, Sathiaseelan A, Crowcroft J.
\newblock Exploiting the power of multiplicity: a holistic survey of
  network-layer multipath.
\newblock IEEE Comm Surv Tut. 2015;17(4):2176--2213.

\bibitem{khiani_comparative_2013}
Khiani SR, Dethe C, Thakare V.
\newblock Comparative {Analysis} of {Multipath} {Routing} {Techniques} and
  {Design} of {Secure} {Energy} {Aware} {Routing} {Algorithm} for {Wireless}
  {Sensor} {Network}.
\newblock IJACR. 2013;3(3):374.

\bibitem{kshemkalyani_distributed_2008}
Kshemkalyani AD, Singhal M.
\newblock Distributed computing: principles, algorithms, and systems.
\newblock Cambridge University Press; 2008.

\bibitem{lua_survey_2005}
Lua EK, Crowcroft J, Pias M, Sharma R, Lim S.
\newblock A survey and comparison of peer-to-peer overlay network schemes.
\newblock IEEE Commun Surv Tut. 2005;7(2):72--93.

\bibitem{korzun_structured_2013}
Korzun D, Gurtov A.
\newblock Structured peer-to-peer systems: fundamentals of hierarchical
  organization, routing, scaling, and security.
\newblock New York, NY: Springer; 2013.

\bibitem{mohr_explaining_1982}
Mohr LB.
\newblock Explaining organizational behavior.
\newblock Jossey-Bass; 1982.

\bibitem{walker_mass_2012}
Walker DC.
\newblock Mass notification and crisis communications: {Planning},
  preparedness, and systems.
\newblock CRC Press; 2012.

\bibitem{nickerson_thinking_2010}
Nickerson JV, Tversky B, Corter JE, Yu L, Mason D.
\newblock Thinking with networks.
\newblock In: {CogSci}. vol.~36; 2010.

\bibitem{ellison_ten_2000}
Ellison C, Schneier B.
\newblock Ten risks of {PKI}: {What} you're not being told about public key
  infrastructure.
\newblock Comput Secur J. 2000;16(1):1--7.

\bibitem{levien_attack-resistant_2009}
Levien R.
\newblock Attack-resistant trust metrics.
\newblock In: Computing with {Social} {Trust}. Springer; 2009. p. 121--132.

\bibitem{reiter_resilient_1998}
Reiter MK, Stubblebine SG.
\newblock Resilient authentication using path independence.
\newblock IEEE T Comput. 1998;47(12):1351--1362.

\bibitem{lamport_byzantine_1982}
Lamport L, Shostak R, Pease M.
\newblock The {Byzantine} generals problem.
\newblock TOPLAS. 1982;4(3):382--401.

\bibitem{castro_practical_1999}
Castro M, Liskov B, {others}.
\newblock Practical {Byzantine} fault tolerance.
\newblock In: {OSDI}. vol.~99; 1999. p. 173--186.

\bibitem{dwork_pricing_1993}
Dwork C, Naor M.
\newblock Pricing via processing or combatting junk mail.
\newblock In: Advances in {Cryptology}. Springer; 1993. p. 139--147.

\bibitem{nakamoto_bitcoin:_2008}
Nakamoto S.
\newblock Bitcoin: {A} peer-to-peer electronic cash system.
\newblock bitcoinorg. 2008; p.~28.

\bibitem{mazieres_stellar_2015}
Mazières D.
\newblock Stellar {Consensus} {Protocol}: {A} {Federated} {Model} for
  {Internet}-level {Consensus}; 2015.

\bibitem{fiat_censorship_2002}
Fiat A, Saia J.
\newblock Censorship resistant peer-to-peer content addressable networks.
\newblock In: {SIAM} {SODA}. ACM; 2002. p. 94--103.

\bibitem{clarke_freenet:_2001}
Clarke I, Sandberg O, Wiley B, Hong TW.
\newblock Freenet: {A} distributed anonymous information storage and retrieval
  system.
\newblock In: Designing {Privacy} {Enhancing} {Technologies}. Springer; 2001.
  p. 46--66.

\bibitem{shamir_how_1979}
Shamir A.
\newblock How to share a secret.
\newblock Communications of the ACM. 1979;22(11):612--613.

\bibitem{blakley_safeguarding_1979}
Blakley GR.
\newblock Safeguarding cryptographic keys.
\newblock P Natl Comp Conf. 1979;48:313--317.

\bibitem{zhang_using_2002}
Zhang H, Goel A, Govindan R.
\newblock Using the small-world model to improve freenet performance.
\newblock In: {INFOCOM}. vol.~3. IEEE; 2002. p. 1228--1237.

\bibitem{kleinberg_small-world_2000}
Kleinberg J.
\newblock The small-world phenomenon: {An} algorithmic perspective.
\newblock In: {STOC}. ACM; 2000. p. 163--170.

\bibitem{alrajeh_secure_2013}
Alrajeh NA, Alabed MS, Elwahiby MS.
\newblock Secure ant-based routing protocol for wireless sensor network.
\newblock Int J Distrib Sens N. 2013;2013.

\bibitem{kohno_improvement_2012}
Kohno E, Okazaki T, Takeuchi M, Ohta T, Kakuda Y, Aida M.
\newblock Improvement of assurance including security for wireless sensor
  networks using dispersed data transmission.
\newblock J Comp Sys Sci. 2012;78(6):1703--1715.

\bibitem{khalil_unmask:_2010}
Khalil I, Bagchi S, Rotaru CN, Shroff NB.
\newblock {UnMask}: {Utilizing} neighbor monitoring for attack mitigation in
  multihop wireless sensor networks.
\newblock Ad Hoc Networks. 2010;8(2):148--164.

\bibitem{lou_h-spread:_2006}
Lou W, Kwon Y.
\newblock H-{SPREAD}: a hybrid multipath scheme for secure and reliable data
  collection in wireless sensor networks.
\newblock IEEE T Veh Technol. 2006;55(4):1320--1330.

\bibitem{liu_secure_2012}
Liu A, Zheng Z, Zhang C, Chen Z, Shen X.
\newblock Secure and energy-efficient disjoint multipath routing for {WSNs}.
\newblock IEEE T Veh Technol. 2012;61(7):3255--3265.

\bibitem{leskovec_graphs_2005}
Leskovec J, Kleinberg J, Faloutsos C.
\newblock Graphs over time: densification laws, shrinking diameters and
  possible explanations.
\newblock In: Proceedings of the eleventh {ACM} {SIGKDD} international
  conference on {Knowledge} discovery in data mining. ACM; 2005. p. 177--187.

\bibitem{xu_internet_2011}
Xu X, Mao ZM, Halderman JA.
\newblock Internet censorship in {China}: {Where} does the filtering occur?
\newblock In: International {Conference} on {Passive} and {Active} {Network}
  {Measurement}. Springer; 2011. p. 133--142.

\bibitem{dingledine_tor:_2004}
Dingledine R, Mathewson N, Syverson P.
\newblock Tor: {The} second-generation onion router.
\newblock DTIC Document; 2004.

\end{thebibliography}

\end{document}

>>>>

\documentclass{sig-alternate-05-2015}

\usepackage[utf8]{inputenc}
\usepackage{afterpage}
\usepackage{epigraph}
\usepackage{tikz}
\usepackage{soul}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{arrows,chains,decorations.pathreplacing}
\usepackage{pifont} % http://ctan.org/pkg/pifont
\usepackage{float}

@@

\begin{document}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{}

% ISBN
\isbn{}

%Conference
\conferenceinfo{Pre-print}{Currently under peer review.}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Edward L. Platt \\
\affaddr{University of Michigan}\\
\email{elplatt@umich.edu}
\alignauthor
Daniel M. Romero \\
\affaddr{University of Michigan}\\
\email{drom@umich.edu}
}
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{1932 Wallamaloo Lane}\\
%       \affaddr{Wallamaloo, New Zealand}\\
%       \email{trovato@corporation.com}
% 2nd. author
%\alignauthor
%G.K.M. Tobin\titlenote{The secretary disavows
%any knowledge of this author's actions.}\\
%       \affaddr{Institute for Clarity in Documentation}\\
%       \affaddr{P.O. Box 1212}\\
%       \affaddr{Dublin, Ohio 43017-6221}\\
%       \email{webmaster@marysville-ohio.com}
% 3rd. author

\maketitle
\begin{abstract}
It is crucial for large-scale communication networks such as the internet
to be resilient against attacks\cite{sterbenz_resilience_2010}
such as censorship and surveillance,
which pose a threat to free expression and free association.
Self-organized networks such as the internet’s router network typically have
heavy-tailed degree distributions\cite{barabasi_scale-free_2009},
making them highly vulnerable to targeted attacks against central nodes
\cite{albert_error_2000}.
While cryptographic solutions exist,
they fail to address the underlying topological problem,
and remain vulnerable to
man-in-the-middle attacks \cite{nayak_different_2010}
and coercion \cite{grewal_caveat_2013}.
Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We present a novel concurrent multipath routing (CMR) algorithm for the
wraparound butterfly network topology,
as well as a highly attack-tolerant Structured Multipath Fault Tolerance (SMFT)
architecture which incorporates the butterfly CMR algorithm. We also identify a
previously unexplored relationship between network topology, trust transitivity,
and attack-tolerance, and provide a framework for further exploration of this
relationship. Our work is the first theoretical demonstration of a point-to-point
communication network architecture that can resist coercion and other
non-technical attacks, without requiring infinitely transitive trust.
To address cases where the network structure cannot be fully controlled,
we demonstrate how a snapshot of the internet’s router network can be partially
rewired for greater attack-tolerance.
More broadly, we hope that this work will serve as a starting point for the
evelopment of additional topology-based attack-tolerant communication
architectures to guard against the dangers of censorship and surveillance.
\end{abstract}

\section*{Introduction}

@@

\begin{figure}[H]
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
A small increase in the number of utilized paths (network traffic)
can compensate for a large increase in attacker power.
}
\label{fig:pfail}
\end{figure}

@@

We define the {\em bounded trust model} (Fig. \ref{fig:trust-source}) on
an undirected graph $G = (V,E)$,
although the model can easily be extended to directed multigraphs.
Vertices representing communicating parties,
with edges representing mutually trusted communication links.
We define a {\em trust radius} $h$ such that nodes $v$ and
$w$ trust each other if their distance is less than $h$.
For a given node $v$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
and if compromised can entirely isolate $v$ from the rest of the network.

\begin{figure}[H]
\centerline{\includegraphics[width=4in,height=2.78in]{fig-partial-trust.pdf}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[height=3in]{fig-bf-route}
\end{center}
\caption{
A 3-dimensional wrap-around butterfly network.
Note that the rightmost nodes are the same nodes as the leftmost,
drawn twice for visual clarity.
The highlighted nodes and edges show the path from node (0,000)
to node (1,101).
\label{fig:bf-route}
}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics{fig-diameter}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The original network fragments when the top 1\% of nodes are removed.
With only 10\% of the butterfly edges present,
this value doubles to 2\%.
With 90\% of the edges rewired,
the network remains unfragmented beyond the failure of the 8\% most
central nodes.
The rewiring scheme does not require adding any additional edges.
}
\label{fig:diameter}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=5in,height=5in]{fig-mincut}}
\caption{
Simulation of targeted attacks against a snapshot of the internet's router
network with a fraction of the edges rewired into a partial butterfly configuration.
The effective redundancy is shown for several values of trust transitivity $h$.
For $h>0$, the original network has higher effective redundancy up to a crossover point,
after which the rewired network performs better.
}
\label{fig:mincut}
\end{figure}

@@

\begin{figure}[H]

@@

\begin{figure}[H]
\begin{center}
\includegraphics{fig-routing}
\end{center}
\caption{
An example of one path as constructed by the proposed multipath
routing algorithm.
The path is shown for $s = 10_2$
and $w = (6, 0110111_2)$.
\label{fig:routing}
}
\end{figure}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%
\end{document}
